A few stickleback can transport adaptive alleles to new lakes

### 2019-05-08 Stickleback_Paper.tex
updated readme to include acstract

%\singlespacing
\onehalfspacing
%\doublespacing

@@

\newcommand{\plr}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}
\newcommand{\jgg}[1]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=black]{#1}}
\newcommand{\bill}[1]{\todo[linecolor=green,backgroundcolor=yellow!25,bordercolor=black]{#1}}

@@

% Jared's general notes for formatting
% - ``citep'' for ``cite in parentheses''. (and, citations come before the punctuation)
% - in latex, use ` `words' ' to get the open- and closed-double quotes (not the double-quote character)
% - "citet" for "cite, as part of the text"

@@

%\plr{I like the spirit of the first paragraph, but want to totally rewrite it}
%\wac{I did a little editing but Peter can still totally rewrite. Regardless it needs to be streamlined a fair bit}

@@

%%%%%%%%%%%%%%%%

@@

We also used neutral mutations to calculate $F_{ST}$, calculated on a per-locus basis and then averaged in windows as a measure of between-population relative differentiation. Concretely, if $p_f$ and $p_m$ are the frequencies of a given mutant allele in the freshwater and marine habitats, respectively, and $\bar p = (p_f + p_m)/2$, then we compute $F_{ST}$ for that mutation as $1 - p_f p_m / (\bar p (1-\bar p))$.

%%%%%%%%%%%%%%%%%%
\section*{Results}

@@

%%%%%%%%%%%%
\subsection*{Local Adaptation: differentiation with gene flow}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{Final_Plots/Fst_Genome_faa.pdf}
          \caption{
        Average $F_{ST}$ in windows of 500Mb between:
                \textbf{(top)} marine habitat and old lakes;
                \textbf{(middle)} marine habitat and new lakes; and
                \textbf{(bottom)} old and new lakes.
                Each plot shows $F_{ST}$ values for a separate simulation,
                with columns corresponding to increasing gene flow from left to right.
        $F_{st}$ is calculated between all marine individuals, and all lakes pooled together.
        %Ten vertical dotted pink lines in each subplot 
                %show regions which have the potential to affect phenotype.
        All locations of pre-existing freshwater adapted alleles have been highlighted by 
        pink dashed vertical lines with an alpha value of 0.3, so darker shades of pink imply more 
        freshwater adapted alleles at that location.
     } \label{fig:Fst}
    \end{center}
\end{figure}

@@

%\begin{comment}
%\paragraph{Standing genetic variation} 
%Despite a dramatic difference in the amount of allelic sharing between lakes, 
%standing genetic variance (Figure \ref{fig:SGV}) 
%was around 0.05 in the freshwater habitat across all but the highest migration rates. 
%Concurrently, genetic variation in the marine population 
%steadily increased with migration to a similar value. 
%On the one hand, it is not surprising that lakes, as a group, 
%carry more genetic variation than the marine habitat, 
%since population subdivision allows different alleles to become common in each. 
%However, it is striking that at $m=.005$, 
%the marine habitat carries as much genetic variation, 
%despite a lack of any substantial migration load.
%\plr{perhaps we want to remove this bit? revisit if it is telling us something important.}
%\end{comment}

%%%%%%%%%%%%
\subsection*{Scans for selection}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrr}
      \hline
     & m=0.01 & m=0.1 & m=1 & m=10 \\ 
      \hline
          best & 2.77 & -12.02 & -21.02 & -7.02 \\ 
      % expected & 4.22 & -4.78 & -14.64 & -5.47 \\ 
       \hline
    \end{tabular}
    \caption{
        Haplotypic variation present in the new lakes at time of colonization,
        across rates of gene flow,
        % \textbf{``Best''} 
        quantified as the most negative trait value achievable
            with intact haplotypes, averaged across populations
            (see text for details).
        % \textbf{``Expected''} shows the trait value
        %     achieved by averaging haplotypic values weighted by fitness
        %     (see text for details).
    } \label{tab:linkage}
\end{table}

@@

%%%%%%%%%%%%
\subsection*{Theoretical expectations}

@@

%%%%%%%%%%%%%%%%%%%%
\section*{Discussion}

>>>>

\onehalfspacing

@@

\newcommand{\plr}[1]{\todo[linecolor=blue,backgroundcolor=blue!25,bordercolor=blue]{#1}}
\newcommand{\jgg}[1]{\todo[linecolor=green,backgroundcolor=green!25,bordercolor=black]{#1}}
\newcommand{\wac}[1]{\todo[linecolor=green,backgroundcolor=yellow!25,bordercolor=black]{#1}}

@@

@@

\plr{I like the spirit of the first paragraph, but want to totally rewrite it}
\wac{I did a little editing but Peter can still totally rewrite. Regardless, it needs to be streamlined a fair bit}

@@

@@

We used neutral mutations to calculate $F_{ST}$, calculated on a per-locus basis and then averaged in windows as a measure of between-population relative differentiation. Concretely, if $p_f$ and $p_m$ are the frequencies of a given mutant allele in the freshwater and marine habitats, respectively, and $\bar p = (p_f + p_m)/2$, then we compute $F_{ST}$ for that mutation as $1 - p_f p_m / (\bar p (1-\bar p))$.

\section*{Results \& Discussion}

@@

\subsection*{Local Adaptation: differentiation with gene flow}

@@

\begin{figure}
    \begin{center}
        \includegraphics[width=\textwidth]{Final_Plots/Fst_Genome_faa.pdf}
          \caption{
        Average $F_{ST}$ in windows of 500Mb between:
        \textbf{(top)} marine habitat and old lakes;
        \textbf{(middle)} marine habitat and new lakes; and
        \textbf{(bottom)} old and new lakes.
        Each plot shows $F_{ST}$ values for a separate simulation,
        with columns corresponding to increasing gene flow from left to right.
        $F_{st}$ is calculated between all marine individuals, and all lakes pooled together.
        All locations of pre-existing freshwater adapted alleles have been highlighted by 
        pink dashed vertical lines with an alpha value of 0.3, so darker shades of pink imply more 
        freshwater adapted alleles at that location.
     } \label{fig:Fst}
    \end{center}
\end{figure}

@@

\subsection*{Scans for selection}

@@

\begin{table}[ht]
    \centering
    \begin{tabular}{rrrrr}
      \hline
     & m=0.01 & m=0.1 & m=1 & m=10 \\ 
      \hline
          best & 2.77 & -12.02 & -21.02 & -7.02 \\ 
      % expected & 4.22 & -4.78 & -14.64 & -5.47 \\ 
       \hline
    \end{tabular}
    \caption{
        Haplotypic variation present in the new lakes at time of colonization,
        across rates of gene flow,
        \textbf{``Best''} 
        quantified as the most negative trait value achievable
        with intact haplotypes, averaged across populations
        (see text for details).
    } \label{tab:linkage}
\end{table}

@@

\subsection*{Theoretical expectations}

@@

%%%%%%%%%%%%%%%%%%%%
\section*{Summary}
